\thetitle

### 2008-01-21 models.tex
The Traffic Object Model section is written now.
Had to rearrange the properties and models tables.

\raisebox{1.5pt}{$\centerdot$} generic flows assigned to nodes by sampling [TODO---more detail] \\
\raisebox{1.5pt}{$\centerdot$} session start time randomly assigned from pool of trace session start times

@@

\raisebox{1.5pt}{$\centerdot$} generic flows assigned to nodes according to fitted BiPareto model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} session start time assigned according to Poisson arrival model\raisebox{1.5pt}{\scriptsize*}

@@

\raisebox{1.5pt}{$\centerdot$} all nodes have average number of generic flows \\
\raisebox{1.5pt}{$\centerdot$} session start times uniformly cover viable range

@@

\multirow{11}{*}[2.5pt]{\class{Flow}}

@@

@@

\raisebox{1.5pt}{$\centerdot$} flow size and start time taken from trace \\
\raisebox{1.5pt}{$\centerdot$} overrides distributions of size/interval packet behaviors with flow-specific versions

@@

\raisebox{1.5pt}{$\centerdot$} flow size is sampled from inherited distribution of flow sizes \\
\raisebox{1.5pt}{$\centerdot$} start time relative to previous session flow sampled from inherited distribution \\
\raisebox{1.5pt}{$\centerdot$} inherits distributions of size/interval packet behaviors from destination node

@@

\raisebox{1.5pt}{$\centerdot$} flow size is sampled from fitted BiPareto model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} start time relative to previous flow in session sampled from fitted Lognormal model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} inherits distributions of size/interval packet behaviors from destination node

@@

\raisebox{1.5pt}{$\centerdot$} all flows have size equal to inherited mean \\
\raisebox{1.5pt}{$\centerdot$} average inter-flow interval used between all flows \\
\raisebox{1.5pt}{$\centerdot$} inherits distributions of size/interval packet behaviors from destination node

>>>>

\raisebox{1.5pt}{$\centerdot$} session start time randomly assigned from pool of trace session start times \\
\raisebox{1.5pt}{$\centerdot$} nodes assigned as flow end-points by sampling from inherited src/dst distributions

@@

\raisebox{1.5pt}{$\centerdot$} session start time assigned according to Poisson arrival model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} nodes assigned as flow end-points by sampling from fitted BiPareto model\raisebox{1.5pt}{\scriptsize*}

@@

\raisebox{1.5pt}{$\centerdot$} session start times selected uniformly from viable range \\
\raisebox{1.5pt}{$\centerdot$} nodes have the mean number of generic flows

@@

\multirow{14}{*}[2.5pt]{\class{Flow}}

@@

\raisebox{1.5pt}{$\centerdot$} flow start time and size taken from trace \\

@@

\raisebox{1.5pt}{$\centerdot$} overrides distributions of size/interval packet behaviors with flow-specific versions \\
\raisebox{1.5pt}{$\centerdot$} packet stream from trace file

@@

\raisebox{1.5pt}{$\centerdot$} start time relative to previous flow sampled from inherited distribution \\
\raisebox{1.5pt}{$\centerdot$} flow size sampled from inherited distribution of flow sizes \\
\raisebox{1.5pt}{$\centerdot$} inherits distributions of size/interval packet behaviors from destination node \\
\raisebox{1.5pt}{$\centerdot$} generic packets generated until flow size exhausted

@@

\raisebox{1.5pt}{$\centerdot$} start time relative to previous flow sampled from fitted Lognormal model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} flow size sampled from fitted BiPareto model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} inherits distributions of size/interval packet behaviors from destination node \\
\raisebox{1.5pt}{$\centerdot$} generic packets generated until flow size exhausted

@@

\raisebox{1.5pt}{$\centerdot$} start time relative to previous flow equals mean inherited inter-flow interval \\
\raisebox{1.5pt}{$\centerdot$} all flows have size equal to inherited mean flow size \\
\raisebox{1.5pt}{$\centerdot$} inherits distributions of size/interval packet behaviors from destination node \\
\raisebox{1.5pt}{$\centerdot$} generic packets generated until flow size exhausted

### 2008-01-21 paper.tex
The Traffic Object Model section is written now.
Had to rearrange the properties and models tables.

\newcommand{\Section}[1]{\hyperref[sec:#1]{Section~\ref*{sec:#1}}}
\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsf{\small{#1}}}
\newcommand{\submodel}[1]{\textsf{\small{#1}}}
\newcommand{\model}[1]{#1}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

%\begin{table*}
%\begin{center}\small
%\input{models.tex}
%\caption{The three levels of traffic behavior and the traffic models defined for each level.}\label{tab:traffic-models}
%\end{center}
%\vspace{-1.75em}
%\end{table*}

@@

\begin{table}[t]
\vspace{0.75em}
\begin{center}
\begin{tabular}[t]{|l|}
\hline
\begin{minipage}[l]{2.8in}
\begin{small}
\vspace{0.6em}
\input{properties.tex}
\vspace{0.6em}
\end{small}
\end{minipage}
\\\hline
\end{tabular}
\end{center}
\vspace{-0.5em}
\caption{Classes and their properties in the Traffic Object Model.}
\vspace{-2em}
\end{table}

\subsection{The Traffic Object Model~(\caps{TOM})}\label{sec:models}

\begin{table*}[t]
\begin{center}
\small
\input{models.tex}
\footnotesize\\[0.5em]
\raisebox{1pt}{*}Parametric models fitted to inherited empirical distributions using maximum likelihood estimation ({\scriptsize{MLE}}).
\end{center}
\vspace{-0.75em}
\caption{Summary of how the sub-models at each behavioral level of the {\footnotesize{TOM}} delegate, override or inherit properties.}
\vspace{-1.75em}
\end{table*}

>>>>

\newcommand{\Section}[1]{\hyperref[sec:#1]{Section~\ref*{sec:#1}}}
\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsf{\footnotesize{#1}}}
\newcommand{\submodel}[1]{\textsf{\footnotesize{#1}}}
\newcommand{\model}[1]{#1}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

@@

\begin{table}[t]
\vspace{0.75em}
\begin{center}
\begin{tabular}[t]{|l|}
\hline
\begin{minipage}[l]{2.7in}
\begin{small}
\vspace{0.6em}
\input{properties.tex}
%\vspace{0.6em}
\end{small}
\end{minipage}
\\\hline
\end{tabular}
\end{center}
\vspace{-0.5em}
\caption{Classes and their attributes in the Traffic Object Model.}
\vspace{-2em}
\end{table}

\subsection{The Traffic Object Model~(\caps{TOM})}\label{sec:tom}

\begin{table*}[t]
\begin{center}
\small
\input{models.tex}
\footnotesize\\[0.5em]
\raisebox{1pt}{*}Parametric models fitted to inherited empirical distributions using maximum likelihood estimation ({\scriptsize{MLE}}).
\end{center}
\vspace{-0.75em}
\label{fig:properties}
\caption{Summary of how the sub-models at each behavioral level of the {\footnotesize{TOM}} delegate, override or inherit properties.}
\vspace{-1.75em}
\end{table*}

In this section, we present a generic object-oriented framework for implementing traffic generation models. This framework is called the Traffic Object Model (\caps{TOM}). It defines four levels of responsibility: network, node, flow and packet. The framework is designed so that different behaviors at each level can be naturally implemented  as classes in object-oriented programming languages. The framework automatically gains the advantages of object orientation, in particular modularity and encapsulation. Every traffic model is naturally split into separate spheres of responsibility, which constitute sub-models for the aspects of the model's behavior at each layer. Thanks to encapsulation and polymorphism of objects, the sub-models from different models can immediately be recombined to create new hybrid behaviors. It is trivial, for example, to produce trace-based node behavior, coupled with parametric flow behavior, and uniform packet behavior. Not all combinations of sub-models are valid, however; which classes may be combined depends on the details of each class. The ability to mix-and-match aspects of behavior at different levels greatly enhances our ability to explore the space of possible traffic models.

%For example, to use uniform flow behavior but non-uniform, trace-based node behavior, simply mix the the uniform implementation of the

Abstract base classes define the properties at each level that traffic models must implement.\footnote{In Java or C\#, this role may be played either by an actual abstract class or by an interface. In duck-typed languages such as Ruby or Python, no actual abstract class need exist, since type is implicitly defined by usage; if inheritance is desired, the base class can be made abstract by defining stub methods that throw informative exceptions if called.} Figure~\ref{fig:properties} enumerates all the properties exposed by traffic models used in this work. Other traffic models may necessitate exposing additional properties, but this list suffices to implement the models used in this paper. Concrete classes implement the behavior of specific traffic models at each level. A complete synthetic workload is created as follows:
\begin{enumerate}
\item instantiate a \class{Network} object of the appropriate class;
\item the top-level \class{Network} object in turn instantiates a collection of \class{Node} objects and associated \class{Flow} objects;
\item each \class{Flow} object generates a stream of \class{Packet} objects.
\end{enumerate}
The hierarchy of objects may be used to directly drive a simulation, or may generate configuration files that in turn drive a simulation. Our implementation does the latter, generating a collection of Qualnet configuration files and trace files specific to each workload instantiation (see \Section{simulations}).

\subsection{Traffic Models}\label{sec:models}

### 2008-01-21 properties.tex
Finally tweaked the models & properties tables to satisfaction.
The Traffic Object Model section is written now.
Had to rearrange the properties and models tables.

\noindent
\textbf{Network:}
\begin{itemize}
  \item collection of nodes
  \item collection of flows
  \item distribution of flow sizes
  \item distribution of intervals between flow start times
  \item distribution of packet sizes
  \item distribution of inter-packet intervals
\end{itemize}
\noindent
\textbf{Node:}
\begin{itemize}
  \item collection of source flows
  \item collection of destination flows
  \item session start time
  \item distribution of flow sizes
  \item distribution of intervals between flow start times
  \item distribution of packet sizes
  \item distribution of inter-packet intervals
\end{itemize}
\noindent
\textbf{Flow:}
\begin{itemize}
  \item source
  \item destination
  \item start time
  \item size (byte count)
  \item distribution of packet sizes
  \item distribution of inter-packet intervals
\end{itemize}
\noindent
\textbf{Packet:}
\begin{itemize}
  \item send time
  \item payload size (bytes)
\end{itemize}

>>>>

\textbf{\submodel{Network:}}\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~collection of nodes\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~collection of flows\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of flow sizes\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of flow-source counts\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of flow-destination counts\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of intervals between flow start times\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of packet sizes\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of inter-packet intervals\\
\textbf{\submodel{Node:}}\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~session start time\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~collection of source flows\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~collection of destination flows\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of flow sizes\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of intervals between flow start times\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of packet sizes\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of inter-packet intervals\\
\textbf{\submodel{Flow:}}\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~start time\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~source node\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~destination node\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~stream of packets\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of packet sizes\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~distribution of inter-packet intervals\\
\textbf{\submodel{Packet:}}\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~send time\\
\hspace*{1ex}\raisebox{1.5pt}{$\centerdot$}~payload size (bytes)\\
